---
title: "Pitch for COVID-19 Shiny App"
author: "B Harold"
date: "2020-04-03"
output: ioslides_presentation
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
```

## Overview

The purpose of this application is to allow the user to see the recent rate of new COVID-19 cases for any country.

The data has been gathered by the European Centre for Disease Prevention and Control.

The next slides show examples of the charts.

The presentation can be accessed at <https://bharold-ling.shinyapps.io/COVIDRecent/>.


## Example: Cases Reported by Date

```{r results='hide',message=FALSE,warning=FALSE}
library(lubridate)
library(dplyr)
library(ggplot2)
```

```{r dataprep, cache=TRUE}
cov <- readRDS("COVID.Cum.Plot/cov.rds")

last.report <- max(cov$date)

# Sample values
country <- "Spain"
end.new <- last.report
newdays <- 7


# Calculations
start.new <- end.new - newdays + 1

workset1 <- cov %>%
    filter(country == country) %>%
    select(date, cases) %>%
    filter(date <= end.new)
if (nrow(workset1) > 0) {
    workset1$status <- "Previous"
    workset1$status[workset1$date >= start.new] <- "Recent"
} else {
    workset1$status = character()
}
country.df <- workset1
```

### Code

```{r echo=TRUE, eval=FALSE}
ggplot(country.df, aes(date, cases)) + 
            geom_col(aes(fill = status)) +
            scale_color_manual(values = c("#56B4E9", "#D55E00"),
                               aesthetics = c("color", "fill"))
```

## Example: Cases Reported by Date (cont)

Country: `r country`, Report as of: `r end.new`, Number of days for recent: `r newdays`

```{r}
ggplot(country.df, aes(date, cases)) + 
            geom_col(aes(fill = status)) +
            scale_color_manual(values = c("#56B4E9", "#D55E00"), aesthetics = c("color", "fill"))
```

## Example: Proportions

```{r}
        # Donut chart (code adapted from https://www.r-graph-gallery.com/128-ring-or-donut-plot.html)
        
        data <- data.frame(
            category = c("Recent", "Previous"),
            count = c(
                sum(country.df$cases[country.df$status == "Recent"]),
                sum(country.df$cases[country.df$status == "Previous"])
            )
        )
        
        # Compute percentages
        data$fraction <- data$count / sum(data$count)
        
        # Compute the cumulative percentages (top of each rectangle)
        data$ymax <- cumsum(data$fraction)
        
        # Compute the bottom of each rectangle
        data$ymin <- c(0, head(data$ymax, n=-1))
        
        # Compute label position
        data$labelPosition <- (data$ymax + data$ymin) / 2
        
        # Compute a good label
        data$label <- paste0(data$category, " cases: ", data$count, " \n", round(data$fraction * 100, 0), "%")
```

```{r}
gg <- ggplot(data) +
    scale_color_manual(values = c("#56B4E9", "#D55E00"),
                       aesthetics = c("color", "fill")) +
    theme_void() +
    theme(legend.position = "none")
```

```{r echo=TRUE, fig.height=3}
# Partial plotting code
gg + aes(ymax=ymax, ymin=ymin, xmax=4, xmin=3,
         fill=category) +
    geom_rect() +
    geom_text( x=2, aes(y=labelPosition, label=label),
               size=3) +
    coord_polar(theta="y") + xlim(c(-1, 4))
```


